---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Rachel Good"
date: "`r Sys.Date()`"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1
Each row in the Denny's dataset represents a restaurant location in the US. The variables are: Address, City, State, Zip, Latitude, and Longitude.

```{r dennys-data}
data("dennys")
nrow(dennys)
ncol(dennys)
```

### Exercise 2
The rows and columns represent the same things as the dennys dataset in which each row is a location. The column variables are the same.

```{r laquinta-data}
data("laquinta")
nrow(laquinta)
ncol(laquinta)
```

### Exercise 3

There are no Denny's locations outside the US. There are 2 Laquinta locations in Canada, 6 in Mexico, 1 in China, 1 in New Zealand, 1 in Honduras, 3 in Turkey, 1 in UAE, 1 in Chile, and 1 in Columbia - so 17 total locations outside the US. 

### Exercise 4

We could potentially filter for State, but I am not sure how to filter without having to list all 50 US State abbreviations, considering we don't know what was used for non-States without having to manually search the data for State abbreviations we do not recognize.

Another idea would be to filter for locations above or below a certain latitude. 

### Exercise 5
There are no locations outside the US so filtering for state abbreviations, gives us an empty tibble.
```{r non_state_dennys}
dennys %>%
  filter(!(state %in% states$abbreviation))
```

### Exercise 6

```{r dennys_country}
dennys %>%
  mutate(country = "United States")
```

 
### Exercise 7

As mentioned above: There are 2 Laquinta locations in Canada, 6 in Mexico, 1 in China, 1 in New Zealand, 1 in Honduras, 3 in Turkey, 1 in UAE, 1 in Chile, and 1 in Columbia. However, it looks like this data does not include the locations in China, New Zealand, Turkey, or UAE.

### Exercise 8

```{r laquinta_filter_tibble}
laquinta %>%
  filter(!(state %in% states$abbreviation))
```

```{r laquinta_country}
laquinta <- laquinta %>%
  mutate(country = case_when(
    state %in% state.abb     ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    state == "CH"            ~ "Chile", #check this one
    state %in% c("AG", "QR", "NL", "VE", "SL", "PU") ~ "Mexico",
    state == "FM"            ~ "Honduras"))
```
```{r filter_unitedstates}
laquinta <- laquinta %>%
  filter(country == "United States")
```

###Exercise 9

```{r dennys_state_count}
dennys %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation"))
```
```{r laquinta_state_count}
laquinta %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation"))
```
### Exercise 10

```{r establishment_col}
dennys <- dennys %>%
  mutate(establishment = "Denny's")
laquinta <- laquinta %>%
  mutate(establishment = "La Quinta")

dn_lq <- bind_rows(dennys, laquinta)
```

```{r plot_locations}
ggplot(dn_lq, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point()
```

### Exercise 11
Mitch Hedberg's joke does not seem to apply in North Carolina.
```{r NorthCarolina}
dn_lq_nc <- dn_lq %>% 
  filter(state == "NC")
ggplot(dn_lq_nc, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point(alpha = .5)
```

###Exercise 12
Mitch Hedberg's joke appears to apply to Texas, unlike North Carolina.
```{r Texas}
dn_lq_tx <- dn_lq %>% 
  filter(state == "TX")
ggplot(dn_lq_tx, mapping = aes(x = longitude, y = latitude, color = establishment)) +
  geom_point(alpha = .3)
```
