---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Rachel Good"
date: "`r Sys.Date()`"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")
```

### Exercise 1
Each row in the Denny's dataset represents a restaurant location in the US. The variables are: Address, City, State, Zip, Latitude, and Longitude.

```{r dennys-data}
data("dennys")
nrow(dennys)
ncol(dennys)
```

### Exercise 2
The rows and columns represent the same things as the dennys dataset in which each row is a location. The column variables are the same.

```{r laquinta-data}
data("laquinta")
nrow(laquinta)
ncol(laquinta)
```

### Exercise 3

There are no Denny's locations outside the US. There are 2 Laquinta locations in Canada, 6 in Mexico, 1 in China, 1 in New Zealand, 1 in Honduras, 3 in Turkey, 1 in UAE, 1 in Chile, and 1 in Columbia - so 17 total locations outside the US. 

### Exercise 4

We could potentially filter for State, but I am not sure how to filter without having to list all 50 US State abbreviations, considering we don't know what was used for non-States without having to manually search the data for State abbreviations we do not recognize.

Another idea would be to filter for locations above or below a certain latitude. 

### Exercise 5

```{r non_state_dennys}
dn %>%
  filter(!(state %in% states$abbreviation))
```

### Exercise 6

...

 
Add exercise headings as needed.

